### 2025-01-16 skripsi/chapter2.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document
add revisions file, fix chapter headings, fix numbered enumerate lists bodyless heading like on the explanation of the research design, fix reasonable chktex and lacheck complaints

    \For{\(k=0 \to n\)}
    \For{\(l=0 \to n\)}
    \State{\(\Omega_{k,l}\gets K(\vb{X}_k,\vb{X}_l)\)}
    \EndFor{}
    \EndFor{}
    \State{\(\vb{H} \gets \Omega + \frac{\vb{I}}{C}\)}
    % \State $\vb{1} \gets [1,1,...,1]$
    \State{\(\vb{A} \gets [[]]\)}
    \Comment{Construct left-hand side matrix}
    \State{\(\vb{A}_{0,0} \gets 0\)}
    \For{\(k=0 \to n\)}
    \State{\(\vb{A}_{k+1,0} \gets 1\)}
    \State{\(\vb{A}_{0,k+1} \gets 1\)}
    \EndFor{}
    \For{\(k=0 \to n\)}
    \For{\(l=0 \to n\)}
    \State{\(\vb{A}_{k+1,l+1} \gets \vb{H}_{k,l}\)}
    \EndFor{}
    \EndFor{}
    \State{\(\vb{B}\gets []\)}
    \Comment{Construct left-hand side of the equation}
    \State{\(\vb{B}_0 \gets 0\)}
    \For{\(k=0 \to n\)}
    \State{\(\vb{B}_{k+1} \gets \vb{y}_{k}\)}
    \EndFor{}
    \State{\(\vb{A}^{\dagger} \gets leastSquares(\vb{A})\)}
    \Comment{Compute solution using least-squares}
    \State{\(\vb{S} \gets \vb{A}^{\dagger}\vb{B}\)}
    \State{\(b \gets \vb{S}_{0}\)}
    \For{\(k=0 \to n\)}
    \State{\(\vb{\alpha}_{k} \gets \vb{S}_{k+1}\)}
    \EndFor{}
    \State{\textbf{return}\(\vb{\alpha}, b\)}
    \EndProcedure{}
  \end{algorithmic}
\end{algorithm}

After training the model can be used for prediction of unseen features. The pseudocode for prediction is shown in \lccref{alg:lssvr_prediction} for prediction features \(\vb{U}\) with \(p \) samples. The trained model uses the training features themselves \(\vb{X}\) with \(n \) samples, the learned multipliers of training points \(\vb{\alpha}\), and the bias \(b\).
\begin{algorithm}[H]
  \caption{LSSVR Prediction}\label{alg:lssvr_prediction}
  \begin{algorithmic}[1]
    \Require{\(\vb{U}, \vb{\alpha}, \vb{X}, b\)}
    \Ensure{\(\vb{v}\)}
    \State{\(\Omega \gets [[]]\)} \Comment{Construct matrix of inner products in high dimensional space}

    \For{\(k=0 \to p\)}
    \For{\(l=0 \to n\)}
    \State{\(\Omega_{k,l}\gets K(\vb{U}_{k},\vb{X}_l)\)}
    \EndFor{}
    \EndFor{}
    \State{\(\vb{v} \gets \Omega\vb{\alpha} + \vb{1}_{m}b\)}
  \end{algorithmic}
\end{algorithm}

The choice of kernel used to construct the kernel matrix is problem specific. Three kernels are most commonly used in SVMs. These kernels are:
\begin{enumerate}
  \item Linear Kernel

        This kernel is the simplest with it being the dot product. It is recommended for cases where the number of features overwhelm the number of samples. The kernel is shown in \lccref{eq:linear_kernel}. Because this kernel operates in the original feature space, it is effective for linear problems.
        \begin{equation}
          K(\vb{x}_k,\vb{x}_l) = \vb{x}_k\cdot\vb{x}_l\label{eq:linear_kernel}
        \end{equation}
  \item Polynomial Kernel

        The polynomial kernel is shown in \lccref{eq:poly_kernel}. This kernel allows the model to learn more complex nonlinear decision boundaries. The parameter \(c\) is a constant and \(d\) is the degree of the polynomial. The degree of the polynomial need to be monitored closely in order to avoid overfitting.
        \begin{equation}
          K\left(\vb{x}_k,\vb{x}_l\right) = \left(\vb{x}_k\cdot\vb{x}_l+c\right)^{d} \label{eq:poly_kernel}
        \end{equation}
  \item Radial Basis Function Kernel

        The RBF kernel is presented in \lccref{eq:rbf_kernel}. This kernel maps the inputs to infinite dimensional space. This enables the SVM to create decision boundaries which are not rigid. The RBF kernel is especially effective for nonlinear relationships between features and labels. The kernel has a parameter \(\sigma \) which is the scale parameter. This parameter affects how the kernel treats structures of different scales in the features. This parameter can be approximated roughly from the average variance of across all features multiplied by the number of features.
        \begin{equation}
          K(\vb{x}_k,\vb{x}_l) = \exp\left(-\frac{\lVert\vb{x}_k,\vb{x}_l\rVert^2}{2\sigma^2}\right) \label{eq:rbf_kernel}
        \end{equation}
\end{enumerate}

@@

\section{Regression Metrics}\label{sec:evaluation_metrics}
\noindent In order to evaluate the prediction of the model, four metrics are used. The metrics are divided into absolute metrics and relative metrics. Absolute metrics require context of scale to interpret their meaning \autocite{botchkarevNewTypologyDesign2019,alpaydinIntroductionMachineLearning2020}. Meanwhile, relative metrics often have a set range of values that it can have. This allows for quick interpretation of the severity of prediction errors. The metrics we discuss here are:
\begin{enumerate}
  \item MSE and RMSE

        The Mean Squared Error (MSE) and its root RMSE, are both very popular metrics. Given target values \(y_i\) and predictions \(y'_i\) such that the difference is \(e_{i} = y'_i-y_i\), the MSE is shown in \lccref{eq:mse}.
        \begin{equation}
          MSE = \frac{1}{n}\sum_{i=1}^{n}e_{i}^{2}\label{eq:mse}
        \end{equation}

        For The RMSE is simply the square root of the MSE\@. The MSE has the property of inflating large errors. The squaring also makes it so that the values are positive. This means that the absolute lowest error value is zero. However, the squaring does complicate the interpretation because the units are no longer the same as the predictions. Here the RMSE comes into play, because of the root square, the units are back to the original target units. This makes the MSE and RMSE very useful.
  \item MAE

        The second metric is the MAE\@. This metric is calculated as the mean of the absolute differences between the prediction and the target. The MAE is calculated as shown in \lccref{eq:mae}.
        \begin{equation}
          MAE = \frac{1}{n}\sum_{i=1}^{n}\abs{e_{i}}\label{eq:mae}
        \end{equation}

        This metric is good at representing the errors without any distortions. Because there is no nonlinear components, the metric is very straightforward to interpret. Due to the use of the absolute value, the minimum value of the metric is also zero.
  \item R\textsuperscript{2}

        The third metric is the coefficient of determination. This metric can be seen as the ratio between the model's accuracy and a baseline model of mean values. Mathematically, this metric is calculated using \lccref{eq:r2} given target values \(y_i\) and predictions \(y'_i\).
        \begin{equation}
          r2 = 1 - \frac{\sum_{i=1}^{n}(y_{i} - y'_{i})^{2}}{\sum_{i=1}^{n}(y_{i} - \bar{y})^{2}}\label{eq:r2}
        \end{equation}

        Because the R\textsuperscript{2} is a relative metric, there is a range of possible values. First, the highest value possible is one. This happens when the predictions are exactly the same as the targets. For predictions that are no better than the average value, the score is zero. Scores below zero mean that the predictions are worse than the average value.
  \item sMAPE

        The final metric is the symmetric Mean Absolute Percentage Error. This metric has a range of values between zero for no error and two for high error. The values can be scaled by multiplying by 100 to obtain the percentages. Given target values \(y_i\) and predictions \(y'_i\) such that the difference is \(e_{i} = y'_i-y_i\), the sMAPE is calculated using \lccref{eq:smape} where \(\epsilon \) is a small value to prevent divisions by zero.
        \begin{equation}
          sMAPE = \frac{2}{N} \sum_{i=1}^{N}\frac{\abs{e_{i}}}{\max(\abs{y_{i}} + \abs{y'_{i}},\epsilon)}
        \end{equation}

@@

\end{enumerate}

>>>>

    \For{\(k=0 \to n\)}
    \For{\(l=0 \to n\)}
    \State{\(\Omega_{k,l}\gets K(\vb{X}_k,\vb{X}_l)\)}
    \EndFor{}
    \EndFor{}
    \State{\(\vb{H} \gets \Omega + \frac{\vb{I}}{C}\)}
    % \State $\vb{1} \gets [1,1,...,1]$
    \State{\(\vb{A} \gets [[]]\)}
    \Comment{Construct left-hand side matrix}
    \State{\(\vb{A}_{0,0} \gets 0\)}
    \For{\(k=0 \to n\)}
    \State{\(\vb{A}_{k+1,0} \gets 1\)}
    \State{\(\vb{A}_{0,k+1} \gets 1\)}
    \EndFor{}
    \For{\(k=0 \to n\)}
    \For{\(l=0 \to n\)}
    \State{\(\vb{A}_{k+1,l+1} \gets \vb{H}_{k,l}\)}
    \EndFor{}
    \EndFor{}
    \State{\(\vb{B}\gets []\)}
    \Comment{Construct left-hand side of the equation}
    \State{\(\vb{B}_0 \gets 0\)}
    \For{\(k=0 \to n\)}
    \State{\(\vb{B}_{k+1} \gets \vb{y}_{k}\)}
    \EndFor{}
    \State{\(\vb{A}^{\dagger} \gets leastSquares(\vb{A})\)}
    \Comment{Compute solution using least-squares}
    \State{\(\vb{S} \gets \vb{A}^{\dagger}\vb{B}\)}
    \State{\(b \gets \vb{S}_{0}\)}
    \For{\(k=0 \to n\)}
    \State{\(\vb{\alpha}_{k} \gets \vb{S}_{k+1}\)}
    \EndFor{}
    \State{\textbf{return} \(\vb{\alpha}, b\)}
    \EndProcedure{}
  \end{algorithmic}
\end{algorithm}

After training the model can be used for prediction of unseen features. The pseudocode for prediction is shown in \lccref{alg:lssvr_prediction} for prediction features \(\vb{U}\) with \(p \) samples. The trained model uses the training features themselves \(\vb{X}\) with \(n \) samples, the learned multipliers of training points \(\vb{\alpha}\), and the bias \(b\).
\begin{algorithm}[H]
  \caption{LSSVR Prediction}\label{alg:lssvr_prediction}
  \begin{algorithmic}[1]
    \Procedure{PredictionLSSVR}{$\vb{U}, \vb{\alpha}, \vb{X}, b $}
    \State{\(\Omega \gets [[]]\)} \Comment{Construct matrix of inner products in high dimensional space}

    \For{\(k=0 \to p\)}
    \For{\(l=0 \to n\)}
    \State{\(\Omega_{k,l}\gets K(\vb{U}_{k},\vb{X}_l)\)}
    \EndFor{}
    \EndFor{}
    \State{\(\vb{v} \gets \Omega\vb{\alpha} + \vb{1}_{m}b\)}
    \State{\textbf{return} \(\vb{v}\)}
    \EndProcedure{}
  \end{algorithmic}
\end{algorithm}

The choice of kernel used to construct the kernel matrix is problem specific. Three kernels are most commonly used in SVMs. These kernels are:
\begin{numdesc}
  \item[Linear Kernel]
  This kernel is the simplest with it being the dot product. It is recommended for cases where the number of features overwhelm the number of samples. The kernel is shown in \lccref{eq:linear_kernel}. Because this kernel operates in the original feature space, it is effective for linear problems.
  \begin{equation}
    K(\vb{x}_k,\vb{x}_l) = \vb{x}_k\cdot\vb{x}_l\label{eq:linear_kernel}
  \end{equation}
  \item[Polynomial Kernel]

  The polynomial kernel is shown in \lccref{eq:poly_kernel}. This kernel allows the model to learn more complex nonlinear decision boundaries. The parameter \(c\) is a constant and \(d\) is the degree of the polynomial. The degree of the polynomial need to be monitored closely in order to avoid overfitting.
  \begin{equation}
    K\left(\vb{x}_k,\vb{x}_l\right) = {\left(\vb{x}_k\cdot\vb{x}_l+c\right)}^{d} \label{eq:poly_kernel}
  \end{equation}
  \item[Radial Basis Function Kernel]

  The RBF kernel is presented in \lccref{eq:rbf_kernel}. This kernel maps the inputs to infinite dimensional space. This enables the SVM to create decision boundaries which are not rigid. The RBF kernel is especially effective for nonlinear relationships between features and labels. The kernel has a parameter \(\sigma \) which is the scale parameter. This parameter affects how the kernel treats structures of different scales in the features. This parameter can be approximated roughly from the average variance of across all features multiplied by the number of features.
  \begin{equation}
    K(\vb{x}_k,\vb{x}_l) = \exp\left(-\frac{\lVert\vb{x}_k,\vb{x}_l\rVert^2}{2\sigma^2}\right) \label{eq:rbf_kernel}
  \end{equation}
\end{numdesc}

@@

\section{Regression Metrics}\label{sec:evaluation_metrics}
\noindent In order to evaluate the prediction of the model, four metrics are used. The metrics are divided into absolute metrics and relative metrics. Absolute metrics require context of scale to interpret their meaning \autocite{botchkarevNewTypologyDesign2019,alpaydinIntroductionMachineLearning2020}. Meanwhile, relative metrics often have a set range of values that it can have. This allows for quick interpretation of the severity of prediction errors. The metrics we discuss here are:
\begin{numdesc}
  \item[MSE and RMSE]
  The Mean Squared Error (MSE) and its root RMSE, are both very popular metrics. Given target values \(y_i\) and predictions \(y'_i\) such that the difference is \(e_{i} = y'_i-y_i\), the MSE is shown in \lccref{eq:mse}.
  \begin{equation}
    MSE = \frac{1}{n}\sum_{i=1}^{n}e_{i}^{2}\label{eq:mse}
  \end{equation}

  For The RMSE is simply the square root of the MSE\@. The MSE has the property of inflating large errors. The squaring also makes it so that the values are positive. This means that the absolute lowest error value is zero. However, the squaring does complicate the interpretation because the units are no longer the same as the predictions. Here the RMSE comes into play, because of the root square, the units are back to the original target units. This makes the MSE and RMSE very useful.
  \item[MAE]
  The second metric is the MAE\@. This metric is calculated as the mean of the absolute differences between the prediction and the target. The MAE is calculated as shown in \lccref{eq:mae}.
  \begin{equation}
    MAE = \frac{1}{n}\sum_{i=1}^{n}\abs{e_{i}}\label{eq:mae}
  \end{equation}

  This metric is good at representing the errors without any distortions. Because there is no nonlinear components, the metric is very straightforward to interpret. Due to the use of the absolute value, the minimum value of the metric is also zero.
  \item[R\textsuperscript{2}]
  The third metric is the coefficient of determination. This metric can be seen as the ratio between the model's accuracy and a baseline model of mean values. Mathematically, this metric is calculated using \lccref{eq:r2} given target values \(y_i\) and predictions \(y'_i\).
  \begin{equation}
    {R}^{2} = 1 - \frac{\sum_{i=1}^{n}{(y_{i} - y'_{i})}^{2}}{\sum_{i=1}^{n}{(y_{i} - \bar{y})}^{2}}\label{eq:r2}
  \end{equation}

  Because the R\textsuperscript{2} is a relative metric, there is a range of possible values. First, the highest value possible is one. This happens when the predictions are exactly the same as the targets. For predictions that are no better than the average value, the score is zero. Scores below zero mean that the predictions are worse than the average value.
  \item[sMAPE]
  The final metric is the symmetric Mean Absolute Percentage Error. This metric has a range of values between zero for no error and two for high error. The values can be scaled by multiplying by 100 to obtain the percentages. Given target values \(y_i\) and predictions \(y'_i\) such that the difference is \(e_{i} = y'_i-y_i\), the sMAPE is calculated using \lccref{eq:smape} where \(\epsilon \) is a small value to prevent divisions by zero.
  \begin{equation}
    sMAPE = \frac{2}{N} \sum_{i=1}^{N}\frac{\abs{e_{i}}}{\max(\abs{y_{i}} + \abs{y'_{i}},\epsilon)}\label{eq:smape}
  \end{equation}

@@

\end{numdesc}

### 2025-01-16 skripsi/chapter3.tex
fix fourier derivatives with periods, fix typos in cover, change judul to lower case and add title case variant, add toc, tof, tot, toa to table of contents, fix font issue with mathptmx, add statement of originality, remove list of notation (for now), fix incorrect statement about burgers eq in ch2, fix sattelite coverage image caption too long, move burgers eq exact solution to ch2, fix figure positioning H not h, reword future work
add revisions file, fix chapter headings, fix numbered enumerate lists bodyless heading like on the explanation of the research design, fix reasonable chktex and

\begin{figure}[h]
      \centering
      \tikzfig{figures/research_design_diagram}
      \caption{Research design diagram}\label{fig:research_design_diagram}
\end{figure}

The study is carried out in 9 main phases. Each phase has a specific aim to accomplish such that the subsequent phases are able to proceed. Each phase is explained as follows:

\begin{enumerate}
      \item Problem Specification

            In this phase, relevant literature of related works and other supporting materials will be reviewed to lay the groundwork of this study. Specifically, the literature review will encompass partial differential equations and their real world associations, traditional methods employed to solve them, systems with partially known or unknown governing equations, machine learning approaches to the problem, least-squares support vector machines, performance metrics and tools that will be used such as the PyTorch library.

      \item Design of Computational Model

            This phase of the study is allocated to the design of the computational model based on the literature that has been reviewed. The design of the overall process includes data retrieval, preprocessing, and the core spectral regression model itself.

      \item Implementation of Computational Model

            After the computational model design is completed, the model is implemented in the Python Language using the PyTorch library as a core component. Implementation of the computational model is done using an iterative software development model. This development model was chosen due to its adaptability to unexpected challenges which is necessary because of the challenges and unknowns with developing a novel method.

      \item Planning of Experimental Scenarios

            To properly gauge the performance of the proposed method at approximating operators, specifically the solution operator of partial differential equations, experimental scenarios are developed in this phase. Specifically, the scenarios serves three goals which are proof of concept or validation that the method is able to learn operators, a case study of a more complex system with real world data, and a using the model as a surrogate. Together, these experimental scenarios determine the applicability of the model to the problem. In addition, the model will be compared to a baseline model in order to put into context the proposed model's performance. In addition, kernel-input correlation matrices and input-Lagrangian multiplier inner product matrix will also be computed.

      \item Data Generation and Retrieval

            This phase of the study is tied to the experimental scenarios that have been developed. After determination of the scenario specifics, the data that will be used for training, validation, and testing of the model in each scenario will be either generated or retrieved from an external source. In addition, in each scenario the hyperparameters of the model will be determined using Bayesian optimization as an alternative to the traditional grid search method.

      \item Data Preprocessing

            The next phase after data generation or retrieval is preprocessing. This is a crucial step in allowing the core LSSVR to learn the mappings in spectral space. In order to do this, the data will need to be reshaped, and important features selected for. Finally, inputs to the LSSVR will need to be normalized or scaled such that the LSSVR model can much more easily learn the data.

      \item Experiments

            This phase of the study executes the experimental scenarios that was determined previously. The preprocessed data will be used in accordance to the preplanned scenarios.

      \item Analysis and Discussion

            The final phase of the study is the analysis and discussion of the results. Analysis of each experimental scenario will assess the extent of the model's capabilities. Another component of the analysis is interpretation the trained model and how it comes to the predictions that it makes. The discussion will also touch on the hyperparameter optimization and comparisons with the baseline model. This will show how the model performs differently compared to the baseline.
\end{enumerate}

@@

This development model was adapted from \textcite{bittnerManagingIterativeSoftware2006}. Each process in the model is explained as follows:
\begin{enumerate}
      \item Initial Planning

            The first process of the iterative development model sets up the parameters for the iterative development. These parameters are the broad scope of the project and initial requirements such as core components like LSSVR\@. The initial requirements are crucial in guiding the rest of the development as more requirements are gathered. The initial planning also determines technical choices like tooling and choice of language. The planning process also includes a rough architecture based in initial requirements.

      \item Requirements

            This process separates out the backlog of requirements into those that will be worked on in the current iteration. These requirements ideally share some functionality in order to allow the same context to be retained within the iteration which reduces the burden of context switching.

      \item Analysis and Design

            This process an analysis of the requirements of the current iteration is performed. This involves determining the constraints and goals for each requirement. Constraints also need to consider previous iterations such that the requirements can be fulfilled effectively and efficiently without regressing progress that has been made such as breaking existing functionality. From this analysis, the design is updated so that the requirement can be fulfilled. The design itself informs how the code should be structured. The interfaces used in the code are also specified.

      \item Implementation

            The implementation process applies the design that has been produced. In addition to implementing the program, this process also implements tests which validate and verify the produced code. In the case of complex pieces of the design, an approach of creating tests and assertions first is taken. This way, the code can be run quickly and fail immediately to allow a quicker convergence on the intended functionality.

      \item Testing and Evaluation

            Once the design is implemented, tests that have been created are run. Each feature is tested in an integrated manner to expedite the process while still providing enough confidence in the software. The results of the testing process are evaluated and any failed tests are resolved whether by reimplementation or reassessment of the correctness of the tests. Any missing functionality or feature discovered during evaluation are added to the backlog of requirements.

      \item Release

            After an iteration, the current version of the software is released. The iterative nature of this development model necessitates the use of a versioning system. As such each release can be identified by a version number loosely based on semantic versioning \autocite{preston-wernerSemanticVersioning200}. This version numbering system consists of major number that indicates breaking changes, minor numbers which indicate features and non-breaking changes, and lastly patch numbers are used for fixes. A version number is read as \verb|MAJOR.MINOR.PATCH|. During active development, only major version 0 will be used to prevent too many major versions. The released software is hosted in its own GitHub repository at \url{https://github.com/nidduzzi/SpectralSVR}.

\end{enumerate}

>>>>

\begin{figure}[H]
      \centering
      \tikzfig{figures/research_design_diagram}
      \caption{Research design diagram}\label{fig:research_design_diagram}
\end{figure}

The study is carried out in 9 main phases. Each phase has a specific aim to accomplish such that the subsequent phases are able to proceed. Each phase is explained as follows:
\begin{numdesc}
      \item[Problem Specification]
      In this phase, relevant literature of related works and other supporting materials will be reviewed to lay the groundwork of this study. Specifically, the literature review will encompass partial differential equations and their real world associations, traditional methods employed to solve them, systems with partially known or unknown governing equations, machine learning approaches to the problem, least-squares support vector machines, performance metrics and tools that will be used such as the PyTorch library.

      \item[Design of Computational Model]
      This phase of the study is allocated to the design of the computational model based on the literature that has been reviewed. The design of the overall process includes data retrieval, preprocessing, and the core spectral regression model itself.

      \item[Implementation of Computational Model]
      After the computational model design is completed, the model is implemented in the Python Language using the PyTorch library as a core component. Implementation of the computational model is done using an iterative software development model. This development model was chosen due to its adaptability to unexpected challenges which is necessary because of the challenges and unknowns with developing a novel method.

      \item[Planning of Experimental Scenarios]
      To properly gauge the performance of the proposed method at approximating operators, specifically the solution operator of partial differential equations, experimental scenarios are developed in this phase. Specifically, the scenarios serves three goals which are proof of concept or validation that the method is able to learn operators, a case study of a more complex system with real world data, and a using the model as a surrogate. Together, these experimental scenarios determine the applicability of the model to the problem. In addition, the model will be compared to a baseline model in order to put into context the proposed model's performance. In addition, kernel-input correlation matrices and input-Lagrangian multiplier inner product matrix will also be computed.

      \item[Data Generation and Retrieval]
      This phase of the study is tied to the experimental scenarios that have been developed. After determination of the scenario specifics, the data that will be used for training, validation, and testing of the model in each scenario will be either generated or retrieved from an external source. In addition, in each scenario the hyperparameters of the model will be determined using Bayesian optimization as an alternative to the traditional grid search method.

      \item[Data Preprocessing]
      The next phase after data generation or retrieval is preprocessing. This is a crucial step in allowing the core LSSVR to learn the mappings in spectral space. In order to do this, the data will need to be reshaped, and important features selected for. Finally, inputs to the LSSVR will need to be normalized or scaled such that the LSSVR model can much more easily learn the data.

      \item[Experiments]
      This phase of the study executes the experimental scenarios that was determined previously. The preprocessed data will be used in accordance to the preplanned scenarios.

      \item[Analysis and Discussion]
      The final phase of the study is the analysis and discussion of the results. Analysis of each experimental scenario will assess the extent of the model's capabilities. Another component of the analysis is interpretation the trained model and how it comes to the predictions that it makes. The discussion will also touch on the hyperparameter optimization and comparisons with the baseline model. This will show how the model performs differently compared to the baseline.
\end{numdesc}

@@

This development model was adapted from \textcite{bittnerManagingIterativeSoftware2006}. Each process in the model is explained as follows:
\begin{numdesc}
      \item[Initial Planning]
      The first process of the iterative development model sets up the parameters for the iterative development. These parameters are the broad scope of the project and initial requirements such as core components like LSSVR\@. The initial requirements are crucial in guiding the rest of the development as more requirements are gathered. The initial planning also determines technical choices like tooling and choice of language. The planning process also includes a rough architecture based in initial requirements.

      \item[Requirements]
      This process separates out the backlog of requirements into those that will be worked on in the current iteration. These requirements ideally share some functionality in order to allow the same context to be retained within the iteration which reduces the burden of context switching.

      \item[Analysis and Design]
      This process an analysis of the requirements of the current iteration is performed. This involves determining the constraints and goals for each requirement. Constraints also need to consider previous iterations such that the requirements can be fulfilled effectively and efficiently without regressing progress that has been made such as breaking existing functionality. From this analysis, the design is updated so that the requirement can be fulfilled. The design itself informs how the code should be structured. The interfaces used in the code are also specified.

      \item[Implementation]
      The implementation process applies the design that has been produced. In addition to implementing the program, this process also implements tests which validate and verify the produced code. In the case of complex pieces of the design, an approach of creating tests and assertions first is taken. This way, the code can be run quickly and fail immediately to allow a quicker convergence on the intended functionality.

      \item[Testing and Evaluation]
      Once the design is implemented, tests that have been created are run. Each feature is tested in an integrated manner to expedite the process while still providing enough confidence in the software. The results of the testing process are evaluated and any failed tests are resolved whether by reimplementation or reassessment of the correctness of the tests. Any missing functionality or feature discovered during evaluation are added to the backlog of requirements.

      \item[Release]
      After an iteration, the current version of the software is released. The iterative nature of this development model necessitates the use of a versioning system. As such each release can be identified by a version number loosely based on semantic versioning \autocite{preston-wernerSemanticVersioning2002023}. This version numbering system consists of major number that indicates breaking changes, minor numbers which indicate features and non-breaking changes, and lastly patch numbers are used for fixes. A version number is read as \verb|MAJOR.MINOR.PATCH|. During active development, only major version 0 will be used to prevent too many major versions. The released software is hosted in its own GitHub repository at \url{https://github.com/nidduzzi/SpectralSVR}.

\end{numdesc}
